---
title: "COMPASS_TEMPEST_Autochamber_SoilFlux_CO2_20260610"
author: "Zoe Read & S. Wilson"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true
---

##Suggestions: 
# May want to develop a function to select the linear portion of fluxes so you don't have to do it manually
# Set a cutoff for when fluxes are so low they can have a low R2


## Set Up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("remotes") # if necessary
#remotes::install_github("COMPASS-DOE/fluxfinder")

library(fluxfinder)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(dplyr)
library(tidyr)
library(patchwork)
library(hms)
library(googledrive)
library(purrr)
library(readr)
library(stringr)

Date <- "20260610"
Date_dashes <- "2026-06-10"

```

## Pull in Raw Datafiles
```{r, echo = FALSE}

# Create temporary download folder
tmp_dir <- file.path(tempdir(), "pulse_downloads_co2")

dir.create(
  tmp_dir,
  recursive = TRUE,
  showWarnings = FALSE
)

# Confirm it exists
dir.exists(tmp_dir)

#link directory to google drive location - ####CHANGE to the download folder####
target_folder <- "https://drive.google.com/drive/folders/12vQiSxn6l4wgJ5tpSI2TNHl7k6Jkx77s"

#filter to necessary files
files_pulse <- drive_ls(
  path = target_folder,
  recursive = TRUE,
  pattern = "TG10.*data")

#download files to local drive
lapply(seq_len(nrow(files_pulse)), function(i) {
  
  drive_download(
    file = files_pulse$id[i],
    path = file.path(tmp_dir, files_pulse$name[i]),
    overwrite = TRUE
  )
  
})


# List extracted 8100 files (full paths)
file.list <- list.files(
  path = tmp_dir,
  pattern = "TG10.*\\.data$",
  full.names = TRUE,
  recursive = TRUE
)

(file.list)


#Read in all the datafiles 

#Control 7810: TG10-01712
#Saltwater 7810: TG10-01746
#Freshwater 7810: TG10-01725
ctrl_file <- file.list[grepl("TG10-01712", file.list)]
alldat_ctrl <- map(ctrl_file, ffi_read_LI7810)|>list_rbind()
alldat_ctrl_date <- alldat_ctrl %>% 
  filter(TIMESTAMP >= paste0(Date_dashes, "00:00:00")) %>% 
  filter(TIMESTAMP <= paste0(Date_dashes, "23:59:59"))

fresh_file <- file.list[grepl("TG10-01725", file.list)]
alldat_fresh <- map(fresh_file, ffi_read_LI7810)|>list_rbind()
alldat_fresh_date <- alldat_fresh %>% 
  filter(TIMESTAMP >= paste0(Date_dashes, "00:00:00")) %>% 
  filter(TIMESTAMP <= paste0(Date_dashes, "23:59:59"))

salt_file <- file.list[grepl("TG10-01746", file.list)]
alldat_salt <- map(salt_file, ffi_read_LI7810)|>list_rbind()
alldat_salt_date <- alldat_salt %>% 
  filter(TIMESTAMP >= paste0(Date_dashes, "00:00:00")) %>% 
  filter(TIMESTAMP <= paste0(Date_dashes, "23:59:59"))

```

## Read in  metadata file and separate by plot - RUN THIS CODE TO EDIT THE METADATA!
```{r, echo = FALSE, message=FALSE}

#read in metadatfile
md <- (here::here("Processed_Data", paste0("COMPASS_TEMPESTX_SoilFluxes_8100_Metadata_processed_", Date, ".csv")))
metadat <- read.csv(md) 

metadat_edited <- metadat %>%
  mutate(
    # Ensure it's a date-time object
    start_time = ymd_hms(start_time), 
    # Extract date
    Date = as.character(date(start_time)),         
    # Extract time
    Time_8100 = format(start_time, "%H:%M:%S"), 
    #Parses the string as "minutes:seconds" and extracts the total duration in seconds from the period
    total_seconds = as.numeric(ms(obs_length)), 
    #Add unique plot ID for each timestamp 
    unique_ID = paste("Collar", label, start_time, sep = "_"), 
    Vtotal_m3 = Vtotal/(100^3)) %>%
  
  
  ####Make changes to metadata####
  mutate(Time_8100 = as_hms(Time_8100)) %>%
  
   ####Adjust time from 8100 to 7810 time
  # mutate(Time_7810 = case_when(
  #   Plot == "Fresh" ~ Time_7810 + 55, 
  #   Plot == "Salt" ~ Time_7810 + 59, 
  #   Plot == "Control" ~ Time_7810 + 40
  #   ) ) %>% 
  
  # Change start time (label is the collar ID, can subtract 10-15 seconds, can also use the unique_ID for a specific collar+date+time combo)
  mutate(
  Time_7810 = 
  case_when(
  label == 13 ~ Time_8100 + 30,
  label == 14 ~ Time_8100 + 30,
  label == 15 ~ Time_8100 + 30,
  label == 16 ~ Time_8100 + 30,
  label == 29 ~ Time_8100 + 30,
  label == 38 ~ Time_8100 + 30,
  label == 40 ~ Time_8100 + 30,
  label == 41 ~ Time_8100 + 30,
  label == 43 ~ Time_8100 + 15,
  label == 44 ~ Time_8100 + 15,
  label == 49 ~ Time_8100 + 15,  
  unique_ID == "Collar_45_2026-06-10 05:47:26" ~ Time_8100 + 15,  
  TRUE ~ Time_8100) ) %>%
  mutate(Time_7810 = hms::as_hms(as.numeric(Time_7810))) %>%
  mutate(Time_7810 = as.character(Time_7810)) %>%

  # Change observation length (a regular observation length is 90 seconds)
  mutate(total_seconds = case_when(
    unique_ID == "Collar_13_2026-06-10 05:57:31" ~ total_seconds - 30,
    unique_ID == "Collar_45_2026-06-10 20:47:25" ~ total_seconds - 10,
    label == 14 ~ total_seconds - 30,
    label == 29 ~ total_seconds - 30,
    label == 40 ~ total_seconds - 30,
    TRUE ~ total_seconds) ) %>%
  
# Change 7820 start time (label is the collar ID, can subtract 10-15 seconds, can also use the unique_ID for a specific collar+date+time combo)
  mutate(
  Time_7820 =  
  case_when(
  label == 13 ~ Time_8100 + 30,
  label == 14 ~ Time_8100 + 30,
  label == 15 ~ Time_8100 + 30,
  label == 16 ~ Time_8100 + 30,
  TRUE ~ Time_8100) ) %>%
  mutate(Time_7820 = hms::as_hms(as.numeric(Time_7820))) %>%
  mutate(Time_7820 = as.character(Time_7820)) %>%
  
  #Add a flag here for times that are changed 
  mutate(flag = case_when(
    as_hms(Time_8100) != as_hms(Time_7810) ~ "Time changed", 
    as_hms(Time_8100) != as_hms(Time_7820) ~ "Time changed", 
    as.numeric(ms(obs_length)) != total_seconds ~ "Time changed", 
    TRUE ~ NA_character_) 
  ) %>%

  #Add a flag here for fluxes that are not usable
  mutate(flag = if_else(unique_ID %in% c(
    "Collar_13_2026-06-10 13:57:31", 
    "Collar_14_2026-06-10 12:00:30"),
    "Flux unusable, remove", flag) )


##Write out edited metadata
write.csv(metadat_edited, file=here::here("Processed_Data", paste0("COMPASS_TEMPESTX_SoilFluxes_8100_Metadata_edited_", Date, ".csv")), row.names = FALSE)           #Change file name


#Control metadata 
ctrl_metadat <- metadat_edited %>%
  filter(Plot == "Control")

#freshwater metadata 
fresh_metadat <- metadat_edited %>%
  filter(Plot == "Fresh") 

#saltwater metadata 
salt_metadat <- metadat_edited %>%
  filter(Plot == "Salt") 

```

######## Control MATCHING ##############

## Match Control metadata to raw data
```{r, echo = FALSE}

#match the metadata to the concentration data 
alldat_ctrl_date$metadat_row <- ffi_metadata_match(
  data_timestamps = alldat_ctrl_date$TIMESTAMP,
  start_dates = ctrl_metadat$Date,
  start_times = ctrl_metadat$Time_7810,
  obs_lengths = ctrl_metadat$total_seconds) 
# head(alldat)

#Set plot, temp, volume, etc. here 
alldat_ctrl_date$Plot <- ctrl_metadat$unique_ID[alldat_ctrl_date$metadat_row]
alldat_ctrl_date$Volume <- ctrl_metadat$Vtotal_m3[alldat_ctrl_date$metadat_row]
alldat_ctrl_date$final_temp <- ctrl_metadat$Tcham[alldat_ctrl_date$metadat_row] #from 8100 file
alldat_ctrl_date$V2_avg <- ctrl_metadat$V2_avg[alldat_ctrl_date$metadat_row] 
alldat_ctrl_date$V3_avg <- ctrl_metadat$V3_avg[alldat_ctrl_date$metadat_row] 
alldat_ctrl_date$V4_avg <- ctrl_metadat$V4_avg[alldat_ctrl_date$metadat_row] 
alldat_ctrl_date$flag <- ctrl_metadat$flag[alldat_ctrl_date$metadat_row] 

ctrl_metadat$metadat_row <- seq_len(nrow(ctrl_metadat))

dat <- alldat_ctrl_date %>% 
  filter(TIMESTAMP > "2026-06-10 00:30:00",
         TIMESTAMP < "2026-06-10 01:30:00") %>%
  mutate(Collar = case_when(
    str_detect(Plot, "Collar_13") ~ "Collar 13",
    str_detect(Plot, "Collar_14") ~ "Collar 14",
    str_detect(Plot, "Collar_15") ~ "Collar 15",
    str_detect(Plot, "Collar_16") ~ "Collar 16",
    str_detect(Plot, "Collar_49") ~ "Collar 49",
    TRUE                          ~ "Other"
  ), 
    Collar = factor(
      Collar,
      levels = c(
        "Collar 13",
        "Collar 14",
        "Collar 15",
        "Collar 16",
        "Collar 49",
        "Other"
      )
    )
  )

ggplot(dat, aes(TIMESTAMP, CO2, colour = Collar)) +
  geom_point() +
  scale_color_manual(
    values = c(
      "Collar 13" = "red",
      "Collar 14" = "orange",
      "Collar 15" = "yellow",
      "Collar 16" = "green",
      "Collar 49" = "blue",
      "Other" = "grey"
    )
  ) +
  theme_classic()

### Need to deal with weird temperatures - probably take the one from the closest reasonable measurement 

#remove the rows that don't match to metadata
alldat_ctrl_date_meta <- alldat_ctrl_date %>%
filter(!is.na(metadat_row))

#can remove any row that have NA's in the CO2 column
alldat_ctrl_date_noNA <- alldat_ctrl_date %>%
filter(!is.na(CO2))

```


######## FRESHWATER MATCHING ##############

## Match Fresh metadata to raw data
```{r, echo = FALSE}

#match the metadata to the concentration data 
alldat_fresh_date$metadat_row <- ffi_metadata_match(
  data_timestamps = alldat_fresh_date$TIMESTAMP,
  start_dates = fresh_metadat$Date,
  start_times = fresh_metadat$Time_7810,
  obs_lengths = fresh_metadat$total_seconds) 
# head(alldat)

#Set plot, temp, volume, etc. here 
alldat_fresh_date$Plot <- fresh_metadat$unique_ID[alldat_fresh_date$metadat_row]
alldat_fresh_date$Volume <- fresh_metadat$Vtotal_m3[alldat_fresh_date$metadat_row]
alldat_fresh_date$final_temp <- fresh_metadat$Tcham[alldat_fresh_date$metadat_row] #from 8100 file
alldat_fresh_date$V2_avg <- fresh_metadat$V2_avg[alldat_fresh_date$metadat_row] 
alldat_fresh_date$V3_avg <- fresh_metadat$V3_avg[alldat_fresh_date$metadat_row] 
alldat_fresh_date$V4_avg <- fresh_metadat$V4_avg[alldat_fresh_date$metadat_row] 
alldat_fresh_date$flag <- alldat_fresh_date$flag[alldat_fresh_date$metadat_row] 

fresh_metadat$metadat_row <- seq_len(nrow(fresh_metadat))

dat <- alldat_fresh_date %>% 
  filter(TIMESTAMP > "2026-06-10 00:00:00",
         TIMESTAMP < "2026-06-10 01:00:00") %>%
  mutate(Collar = case_when(
    str_detect(Plot, "Collar_41") ~ "Collar 41",
    str_detect(Plot, "Collar_42") ~ "Collar 42",
    str_detect(Plot, "Collar_43") ~ "Collar 43",
    str_detect(Plot, "Collar_44") ~ "Collar 44",
    str_detect(Plot, "Collar_40") ~ "Collar 40",
    str_detect(Plot, "Collar_38") ~ "Collar 38",
    str_detect(Plot, "Collar_45") ~ "Collar 45",
    TRUE                          ~ "Other"
  ), 
    Collar = factor(
      Collar,
      levels = c(
        "Collar 41",
        "Collar 42",
        "Collar 43",
        "Collar 44",
        "Collar 40",
        "Collar 38",
        "Collar 45",
        "Other"
      )
    )
  )

ggplot(dat, aes(TIMESTAMP, CO2, colour = Collar)) +
  geom_point() +
  scale_color_manual(
    values = c(
      "Collar 41" = "red",
      "Collar 42" = "orange",
      "Collar 43" = "yellow",
      "Collar 44" = "green",
      "Collar 40" = "purple",
      "Collar 38" = "lightblue",
      "Collar 45" = "blue",
      "Other" = "grey"
    )
  ) +
  theme_classic()


### Need to deal with weird temperatures - probably take the one from the closest reasonable measurement 

#remove the rows that don't match to metadata
alldat_fresh_date_meta <- alldat_fresh_date %>%
filter(!is.na(metadat_row))

#can remove any row that have NA's in the CO2 column
alldat_fresh_date_noNA <- alldat_fresh_date_meta %>%
filter(!is.na(CO2))

```


############### Saltwater Plot ############################

## Match Salt metadata to raw data
```{r, echo = FALSE}

#match the metadata to the concentration data 
alldat_salt_date$metadat_row <- ffi_metadata_match(
  data_timestamps = alldat_salt_date$TIMESTAMP,
  start_dates = salt_metadat$Date,
  start_times = salt_metadat$Time_7810,
  obs_lengths = salt_metadat$total_seconds) 
# head(alldat)

#Set plot, temp, volume, etc. here 
alldat_salt_date$Plot <- salt_metadat$unique_ID[alldat_salt_date$metadat_row]
alldat_salt_date$Volume <- salt_metadat$Vtotal_m3[alldat_salt_date$metadat_row]
alldat_salt_date$final_temp <- salt_metadat$Tcham[alldat_salt_date$metadat_row] #from 8100 file
alldat_salt_date$V2_avg <- salt_metadat$V2_avg[alldat_salt_date$metadat_row] 
alldat_salt_date$V3_avg <- salt_metadat$V3_avg[alldat_salt_date$metadat_row] 
alldat_salt_date$V4_avg <- salt_metadat$V4_avg[alldat_salt_date$metadat_row] 
alldat_salt_date$flag <- alldat_salt_date$flag[alldat_salt_date$metadat_row] 

salt_metadat$metadat_row <- seq_len(nrow(salt_metadat))

dat <- alldat_salt_date %>% 
  filter(TIMESTAMP > "2026-06-10 00:00:00",
         TIMESTAMP < "2026-06-10 01:00:00") %>%
  mutate(Collar = case_when(
    str_detect(Plot, "Collar_29") ~ "Collar 29",
    str_detect(Plot, "Collar_30") ~ "Collar 30",
    str_detect(Plot, "Collar_31") ~ "Collar 31",
    str_detect(Plot, "Collar_32") ~ "Collar 32",
    str_detect(Plot, "Collar_50") ~ "Collar 50",
    str_detect(Plot, "Collar_51") ~ "Collar 51",
    str_detect(Plot, "Collar_52") ~ "Collar 52",
    TRUE                          ~ "Other"
  ), 
    Collar = factor(
      Collar,
      levels = c(
        "Collar 29",
        "Collar 30",
        "Collar 31",
        "Collar 32",
        "Collar 50",
        "Collar 51",
        "Collar 52",
        "Other"
      )
    )
  )

ggplot(dat, aes(TIMESTAMP, CO2, colour = Collar)) +
  geom_point() +
  scale_color_manual(
    values = c(
      "Collar 29" = "red",
      "Collar 30" = "orange",
      "Collar 31" = "yellow",
      "Collar 32" = "green",
      "Collar 50" = "purple",
      "Collar 51" = "lightblue",
      "Collar 52" = "blue",
      "Other" = "grey"
    )
  ) +
  theme_classic()

### Need to deal with weird temperatures - probably take the one from the closest reasonable measurement 

#remove the rows that don't match to metadata 
alldat_salt_date_meta <- alldat_salt_date %>%
filter(!is.na(metadat_row))

#can remove any row that have NA's in the CO2 column 
alldat_salt_date_noNA <- alldat_salt_date_meta %>%
filter(!is.na(CO2))

```


## Combine all the matched data back into one dataframe 
```{r}

alldat <-  bind_rows(alldat_ctrl_date_noNA, alldat_fresh_date_noNA, alldat_salt_date_noNA)

```


## Calculate fluxes 
```{r, echo = FALSE, message = FALSE, warning=FALSE}
#change the units
alldat$CO2_umol <- ffi_ppm_to_umol(alldat$CO2, 
                                   volume = alldat$Volume # m3
                                   )    # degrees C
#> Assuming atm = 101325 Pa
#> Using R = 8.31446261815324 m3 Pa K-1 mol-1

alldat$CO2_umol_m2 <- alldat$CO2_umol / 0.0318

fluxes <- ffi_compute_fluxes(alldat,
                             group_column = "Plot", 
                             time_column = "TIMESTAMP", 
                             gas_column = "CO2_umol_m2", 
                             dead_band = 30) #, c0_band = 5?
# head(fluxes)

#take a look at the fluxes we calculated with R2 
ggplot(fluxes, aes(Plot, lin_flux.estimate, color = lin_r.squared)) +
  geom_point(size=4) + theme_classic() + 
  geom_linerange(aes(ymin = lin_flux.estimate- lin_flux.std.error,
                   ymax = lin_flux.estimate+ lin_flux.std.error)) +
  scale_color_gradientn(colours = c("darkred",  "red", "white","lightblue", "darkblue"),
                        values = c(0, 0.5, 0.6, 0.7, 1)) +
  ylab("CO2 flux (nmol/m2/s)")+ 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) 

#sort fluxes by R2 
fluxes_good <- as.data.frame(subset(fluxes, lin_r.squared >= .90, select = Plot:TIMESTAMP_max))
fluxes_weird <- as.data.frame(subset(fluxes, lin_r.squared < .90, select = Plot:TIMESTAMP_max))

#negative CO2 fluxes
fluxes_negative <- as.data.frame(subset(fluxes,  lin_flux.estimate < 0, select = Plot:TIMESTAMP_max))

#find fluxes that represent the first and fourth quartile of the data 
low <- quantile(fluxes$lin_flux.estimate, 0.05) 
high <- quantile(fluxes$lin_flux.estimate, 0.95) 

fluxes_low <- as.data.frame(subset(fluxes, lin_flux.estimate <= low, select = Plot:TIMESTAMP_max))
fluxes_high <- as.data.frame(subset(fluxes, lin_flux.estimate >= high, select = Plot:TIMESTAMP_max))

tails <- rbind(fluxes_low, fluxes_high)


```

## Check the fluxes for which I changed the start time due to lags or ebullition (recorded in notes of metadata)
```{r, echo=FALSE}

tobechecked <- c()

colnames <- c()

#Loop to run plots above 
for(P in tobechecked){ 
  r1 <- subset(alldat, Plot == P)
  p1 <- ggplot(r1, aes(TIMESTAMP, CO2)) + geom_point() + theme_classic() +
  ylab(expression(paste( CO [2], " (ppm)"))) +
  xlab("Time") + labs(title = P) + 
  geom_smooth(color="red")
  print(p1)
}

#list of the ones that I changed and checked and looked good? 
fixedplots <- c()
  

```


## Spot check a few fluxes with R2 > 0.9
```{r, echo=FALSE, message=FALSE, warning=FALSE}

### pull a random sample of good fluxes to check and plot 
good_plots <- unique(fluxes_good$Plot)

# take a random sample (FALSE so we don't get the same plot twice)
# set.seed(...) to guarantee reproducibility
good_sample <- sample(good_plots, 5, replace=FALSE)

#Empty list to store plots
plot_list <- list()

#Loop to run five random plots subset above 
for(P in good_sample){ 
  r1 <- subset(alldat, Plot == P)
  r1 <- r1[-c(1:30), ]
  
  p1 <- ggplot(r1, aes(TIMESTAMP, CO2)) + geom_point() + theme_classic() +
  ylab(expression(paste( CO [2], " (ppm)"))) +
  xlab("Time") + labs(title = P) + 
  geom_smooth(color="red")
  
  plot_list[[length(plot_list) + 1]] <- p1
}

### number of plots per page
plots_per_page <- 2

# split plots into pages
plot_pages <- split(
  plot_list,
  ceiling(seq_along(plot_list) / plots_per_page)
)

# print each page
for(i in seq_along(plot_pages)) {
  
  print(
    wrap_plots(plot_pages[[i]], ncol = 2)
  )
  
}

####################
```

## Take a look at the bad fluxes <0.9 
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# If a flux was started too early/late, change start time or Obs_length in metadata file and note n the note column
plot_list <- list()

### pull out fluxes with R2 < 0.9 and put them in a list 
bad_plots <- unique(fluxes_weird$Plot)

#Loop to run five random plots subset above 
for(P in bad_plots){ 
  r1 <- subset(alldat, Plot == P)
  r1 <- r1[-c(1:30), ]
  p1 <- ggplot(r1, aes(TIMESTAMP, CO2)) + geom_point() + theme_classic() +
  ylab(expression(paste( CO [2], " (ppm)"))) +
  xlab("Time") + labs(title = P) + 
  geom_smooth(color="red")
  
  plot_list[[length(plot_list) + 1]] <- p1
}

### number of plots per page
plots_per_page <- 2

# split plots into pages
plot_pages <- split(
  plot_list,
  ceiling(seq_along(plot_list) / plots_per_page)
)

# print each page
for(i in seq_along(plot_pages)) {
  
  print(
    wrap_plots(plot_pages[[i]], ncol = 2)
  )
  
}

####################

#Notes on the bad ones 


##Other fluxes have low R squared but are okay

###########################


```

## Look at the really high or really low ones to see if there is a timing issue or something
```{r, echo=FALSE, message=FALSE, warning=FALSE}

plot_list <- list()

### pull out fluxes in the 5% and 95% tails to look at really high and really low 
tail_plots <- unique(tails$Plot)

#Loop to run five random plots subset above 
for(P in tail_plots){ 
  r1 <- subset(alldat, Plot == P)
  r1 <- r1[-c(1:30), ]
  p1 <- ggplot(r1, aes(TIMESTAMP, CO2)) + geom_point() + theme_classic() +
  ylab(expression(paste( CO [2], " (ppm)"))) +
  xlab("Time") + labs(title = P) + 
  geom_smooth(color="red")
  
  plot_list[[length(plot_list) + 1]] <- p1
}

### number of plots per page
plots_per_page <- 2

# split plots into pages
plot_pages <- split(
  plot_list,
  ceiling(seq_along(plot_list) / plots_per_page)
)

# print each page
for(i in seq_along(plot_pages)) {
  
  print(
    wrap_plots(plot_pages[[i]], ncol = 2)
  )
  
}

#would be nice to put on the plot the flux estimate and if it is a high or low or something 
####################


```

## Look at the negative CO2 fluxes
```{r, echo=FALSE, message=FALSE, warning=FALSE}

plot_list <- list()

### pull out negative fluxes and put them in a list 
neg_plots <- unique(fluxes_negative$Plot)

#Loop to run five random plots subset above 
for(P in neg_plots){ 
  r1 <- subset(alldat, Plot == P)
  r1 <- r1[-c(1:30), ]
  p1 <- ggplot(r1, aes(TIMESTAMP, CO2)) + geom_point() + theme_classic() +
  ylab(expression(paste( CO [2], " (ppm)"))) +
  xlab("Time") + labs(title = P) + 
  geom_smooth(color="red")
  
  plot_list[[length(plot_list) + 1]] <- p1
}

### number of plots per page
plots_per_page <- 2

# split plots into pages
plot_pages <- split(
  plot_list,
  ceiling(seq_along(plot_list) / plots_per_page)
)

# print each page
for(i in seq_along(plot_pages)) {
  
  print(
    wrap_plots(plot_pages[[i]], ncol = 2)
  )
  
}

####################Negative CO2 fluxes

```

## Plot all fluxes
```{r, echo=FALSE, message=FALSE, warning=FALSE}

#ffi_qaqc(fluxes, Plot, output_file = "qaqc.html", output_dir = getwd(), open_output = TRUE)

### pull a random sample of good fluxes to check and plot 
#Empty list to store plots
plot_list <- list()

all_plots <- unique(fluxes$Plot)

#Loop to run five random plots subset above 
for(P in all_plots){ 
  r1 <- subset(alldat, Plot == P)
  r1 <- r1[-c(1:30), ]
  p1 <- ggplot(r1, aes(TIMESTAMP, CO2)) + geom_point() + theme_classic() +
  ylab(expression(paste( CO [2], " (ppm)"))) +
  xlab("Time") + labs(title = P) + 
  geom_smooth(color="red")
  
  plot_list[[length(plot_list) + 1]] <- p1
}

### number of plots per page
plots_per_page <- 2

# split plots into pages
plot_pages <- split(
  plot_list,
  ceiling(seq_along(plot_list) / plots_per_page)
)

# print each page
for(i in seq_along(plot_pages)) {
  
  print(
    wrap_plots(plot_pages[[i]], ncol = 2)
  )
  
}

####################


```


## Do some visualization of QAQC plots to assess fluxes  
```{r, echo=FALSE}

p1 <- ggplot(fluxes, aes(lin_flux.estimate, rob_flux.estimate, color = Plot)) +
  geom_point(size=4) + geom_abline() + 
  theme_classic() + 
  labs(title = "A") + 
  ylab(expression(paste( CH [4], " Flux (nmol m"^-2* " s"^-1*") Robust Method"))) +
  xlab(expression(paste( CH [4], " Flux (nmol m"^-2* " s"^-1*") Linear Method"))) +
  guides(color = guide_legend(title = "Plot")) +
  theme(legend.position="none") +
  theme(axis.title.x = element_text(size=12), axis.text = element_text(size=12),
        axis.title.y = element_text(size=12), legend.text=element_text(size=12),
        panel.border = element_rect(colour = "black", fill=NA, linewidth =1), 
        aspect.ratio = 1)
p1


p2 <- ggplot(fluxes, aes(lin_r.squared, poly_r.squared, color = Plot)) +
  geom_point(size=4) + geom_abline() + 
  theme_classic() + 
  xlim(0,1) + ylim(0,1) +
  labs(title = "B") + 
  ylab(expression(paste("R"^2* " Second-Order Polynomial"))) +
  xlab(expression(paste("R"^2* " Linear Model"))) +
  guides(color = guide_legend(title = "Plot")) + 
  theme(legend.position="none") +
  theme(axis.title.x = element_text(size=12), axis.text = element_text(size=12),
        axis.title.y = element_text(size=12), legend.text=element_text(size=12),
        panel.border = element_rect(colour = "black", fill=NA, linewidth =1), 
        aspect.ratio = 1)
p2

p3 <- ggplot(fluxes, aes(lin_flux.estimate, HM81_flux.estimate, color = lin_r.squared )) +
  geom_point(size=4) + geom_abline() + 
  theme_classic() + 
  #xlim(0,50) + #ylim(0,50) +
  labs(title = "C") + 
  ylab(expression(paste( CH [4], " Flux (nmol m"^-2* " s"^-1*") HM1981 Method"))) +
  xlab(expression(paste( CH [4], " Flux (nmol m"^-2* " s"^-1*") Linear Method"))) +
  guides(color = guide_legend(title = "Plot")) + 
  theme(legend.position="right") +
  theme(axis.title.x = element_text(size=12), axis.text = element_text(size=12),
        axis.title.y = element_text(size=12), legend.text=element_text(size=12),
        panel.border = element_rect(colour = "black", fill=NA, linewidth =1), 
        aspect.ratio = 1)
p3

#ggarrange(p1, p2, p3, ncol=3, nrow=1) #, common.legend = TRUE, legend="none")
```

## Pull together dataframe and export for use elsewhere 
```{r, echo=FALSE}

#head(fluxes1)

####Already flagged poor fluxes, negative fluxes, and low r squared fluxes that are actually okay

#make new columns with the plot; zone; replicate 
IDs <- data.frame(do.call('rbind', strsplit(as.character(fluxes$Plot),'_',fixed=TRUE)))
colnames(IDs) <- c("NA",  "label", "StartTime")
# head(IDs)

#rejoin them to the dataframe
allflux <- cbind(IDs, fluxes)

##Add in notes from metadata - add this in when we fix the fluxes
metadat_notes <- metadat_edited[, c("unique_ID", "flag")]
allflux_notes <- allflux %>%
  left_join(metadat_notes, by=c("Plot"="unique_ID"))

allflux_notes$`NA`<- NULL
allflux_notes$`NA`<- NULL

#Change file name
write.csv(allflux_notes, file=here::here("Processed_Data", paste0("COMPASS_TEMPESTX_SoilFluxes_7810_CO2_processed_", Date, ".csv")), row.names = FALSE)         

```

